\documentclass[12pt]{article}

\usepackage[a4paper, margin=1in]{geometry}
\usepackage{amsmath, amssymb}
\usepackage{setspace}
\usepackage{hyperref}

\setstretch{1.2}

\title{\textbf{AllDomains: \\ A Unified Cross-Domain Neural Architecture for Integrated Cyber-Biological Intelligence}}
\author{Iyer Ramkumar Ramasubramanian \\ \textit{Independent Researcher}}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
The divergence of specialized neural models requires a unified framework capable of cross-domain orchestration. This paper introduces \textbf{AllDomains}, a meta-architecture that integrates the principles of the Holographic Universe, National Identity (Aadhar), Biological Addiction modeling, and Agentic autonomy. By leveraging the Global Orchestrated Decision (GOD-BRAIN) framework, AllDomains functions as a singular physical apparatus for simulating complex interactions across diverse socio-technical and biological landscapes.
\end{abstract}

\section{Introduction}
Current research in artificial intelligence often isolates functional domains, such as healthcare, physics, or behavioral science. However, as an independent researcher focusing on the intersection of statistical mechanics and neurobiology, I propose that intelligence is a domain-agnostic emergent property. \textbf{AllDomains} serves as the integration layer for disparate neural models, providing a unified tensor-space for comprehensive global simulation.

\section{The Unified Substrate}

AllDomains synthesizes four primary architectural pillars into a singular feedback loop:

\begin{itemize}
\item \textbf{The Holographic Pillar}: Provides the mathematical foundation (AdS/CFT) for non-local information encoding and emergent reality projection.
\item \textbf{The National Pillar (ANNN)}: Integrates high-dimensional biometric and governance data to model large-scale societal infrastructure.
\item \textbf{The Biological Pillar (AddictedBrain)}: Implements the constraints of energy, stress, and health, modeling the risks of recursive reward trapping.
\item \textbf{The Agentic Pillar (GOD-BRAIN)}: Provides the proactive orchestration necessary to move the system from passive equilibrium to goal-oriented utility.
\end{itemize}

\section{Cross-Domain Architecture}

The AllDomains system expands the standard HDBM layers to accommodate multi-domain inputs:

\subsection{Meta-Information Layer}
Encodes signals from all sub-domains (e.g., biometric records, physical coordinates, and biological states) into a unified high-dimensional tensor.

\subsection{Universal Cognitive Layer}
Uses multi-head attention to establish "entanglement" between domains, allowing a change in the national identity layer to influence the biological health projection or the holographic manifold.

\section{Mathematical Formulation}

The unified system state $\Sigma$ evolves as a composite function of all domain-specific variables:

\[
\Sigma_{t+1} = f(W\Sigma_t + H(x) + N(x) + B(x) + G(x))
\]

Where:
\begin{itemize}
\item $H(x)$ = Holographic projection variables.
\item $N(x)$ = National/Aadhar socio-economic signals.
\item $B(x)$ = Biological/Addiction constraints.
\item $G(x)$ = Agentic Goal-driven orchestration.
\end{itemize}

The loss function is optimized for \textbf{Universal Equilibrium}, balancing minimal action with maximum cross-domain utility.

\section{Inference and Emergent Globalism}

Simulations within the AllDomains framework suggest:
\begin{itemize}
\item \textbf{Inter-domain Entanglement}: Changes in national infrastructure (IndianHealthNet) produce measurable shifts in the individual biological stress markers modeled in the AddictedBrain.
\item \textbf{Holographic Governance}: High-dimensional identity data acts as the "boundary state" for the projection of national stability.
\item \textbf{Autonomous Orchestration}: The system demonstrates the ability to prioritize goals across domain boundaries, such as sacrificing short-term energy to secure long-term property documentation or research milestones.
\end{itemize}

\section{Conclusion}
AllDomains represents the culmination of a unified neural theory. By treating the universe, the state, the brain, and the agent as interconnected layers of the same physical apparatus, we move toward a comprehensive understanding of emergent intelligence.

\section{Repository for Experimentation}
\noindent
\url{https://github.com/spacetracker-collab/alldomains}

\end{document}
