\documentclass[12pt]{article}
\usepackage[a4paper, margin=1in]{geometry}
\usepackage{hyperref}

\begin{document}

\section*{Author Biography}

\noindent \textbf{Iyer Ramkumar Ramasubramanian} is an independent researcher and architect with over 24 years of experience in software development, enterprise architecture, and disruptive technologies. His career spans significant roles in technical leadership and solutioning, with deep expertise in distributed systems, high-dimensional tensor operations, and performance optimization.

\medskip

\noindent Ramkumar’s current research lies at the intersection of neurobiology, statistical mechanics, and artificial intelligence. He is the primary developer of the \textit{Homo Deus Brain Model} (HDBM) and the \textit{GOD-BRAIN} framework, where he explores the formalization of neural networks as physical apparatuses. His work focuses on emergent properties in multi-agent systems, biocentric reality construction, and the application of Graph Neural Networks (GNNs) to model complex cognitive and social structures.

\medskip

\noindent Historically, his contributions include designing AI-driven solutions for robotic process automation (RPA), text mining, and conversational agents. He has previously served as a Research Assistant at SUNY Buffalo’s Center for Relationship Marketing and has extensive experience in the telecommunications and retail database sectors. He continues to contribute to open science, focusing on the development of ethical, high-dimensional social justice models and the advancement of autonomous cognitive systems.

\end{document}
